\section{Experience}

\begin{twenty} % Environment for a list with descriptions
    \twentyitem{2024-}{Tacnode}{Machine Learning Engineer}{
        Built a serverless platform for LLM fine-tuning, test-time training, and inference, integrated with Discord and Hugging Face. Developed a multi-agent agentic system for database engineering. Owned LLMOps/MLOps, DevOps, and observability end-to-end.
    }
    \twentyitem{2023-2024}{Gradient.AI}{Machine Learning Engineer}{
        Designed and shipped serverless fine-tuning and inference API services for large language models (LLMs), enabling elastic scaling in a multi-tenant environment.
    }
    \twentyitem{2019-2022}{Meta Platforms Inc}{Software Developer}{
        Built machine-learning infrastructure for payments fraud detection. Maintained the HHVM open-source branch and Hack standard libraries, ported HHVM to multiple Linux distributions, and built its CI pipeline.
    }
    \twentyitem{2015-2019}{Thoughtworks Inc}{Lead / Senior Consultant}{
        Delivered product line engineering consulting for Huawei and led architecture for Scala projects for RCA. Founded and maintained open-source projects including Binding.scala and DeepLearning.scala.
    }
    \twentyitem{2006-2014}{Various Game Companies}{Game Developer / Tech Lead}{
        Developed and led teams to build multiple game engines, mobile/web/social games, and 3D applications. Key contributions include engine architecture, development tools, CI/CD pipelines, and open-source libraries.
    }
\end{twenty}

\section{Open-source projects}

\begin{twenty}
	\twentyitem{2021-2022}{\href{https://github.com/facebook/hhvm}{HHVM}}{C++/Rust/OCaml}{is Meta's virtual machine to run Hack. I ported the open source branch of HHVM to NixOS and created CI pipeline for building, testing, and packaging HHVM.}
	\twentyitem{since 2018}{\href{https://github.com/ThoughtWorksInc/Dsl.scala}{Dsl.scala}}{Scala}{is a framework to extend Scala language features in libraries. I also ported this framework to Haskell as \href{https://github.com/Atry/Control.Dsl}{Control.Dsl}.}
	\twentyitem{since 2016}{\href{https://github.com/ThoughtWorksInc/DeepLearning.scala}{DeepLearning.scala} and \href{https://github.com/ThoughtWorksInc/Compute.scala/}{Compute.scala}}{Scala}{are libraries for creating complex neural networks.}
	\twentyitem{since 2015}{\href{https://github.com/ThoughtWorksInc/Binding.scala}{Binding.scala}}{Scala}{is a reactive templating language for creating web and desktop GUI.}
	\twentyitem{2015-2016}{\href{https://thoughtworksinc.github.io/microbuilder/1-overview.html}{Microbuilder}}{Haxe / Scala / Java / JavaScript}{is a toolkit to build system across micro-services implemented in various languages communicating via RESTful JSON API.}
	\twentyitem{since 2012}{\href{https://github.com/Atry/haxe-continuation}{haxe-continuation}}{Haxe}{provides \lstinline{async}/\lstinline{await} syntax for Haxe.}
	\twentyitem{since 2010}{\href{https://github.com/Atry/protoc-gen-as3/}{protoc-gen-as3}}{ActionScript3}{is a Protocol Buffers plugin for ActionScript 3.}
	\twentyitem{since 2007}{\href{https://github.com/search?o=desc&q=+user\%3Aatry+user\%3Athoughtworksinc+committer\%3Aatry&s=stars&type=Repositories}{other 100+ of open-source projects}}{}{}
\end{twenty}

\section{Publications}

\begin{twentyshort} % Environment for a short list with no descriptions
	\twentyitem{2025}{\href{https://arxiv.org/abs/2503.01224}{CE-U: Cross Entropy Unlearning}}{first author}{}
	\twentyitem{2017}{\href{https://arxiv.org/abs/2307.12187}{Mondic Deep Learning}}{first author}{}
	\twentyitem{2017}{\href{https://arxiv.org/abs/2307.16073}{Ad-hoc polymorphic delimited continuations
	}}{first author}{}
	\twentyitem{2009}{\href{https://books.google.com/books/about/Flex_3\%E6\%9D\%83\%E5\%A8\%81\%E6\%8C\%87\%E5\%8D\%97.html?id=dNUsQwAACAAJ}{Adobe Flex 3: Training from the Source}}{translator}{}
\end{twentyshort}
\section{Talks}

\begin{twenty}
	\twentyitem{2017}{\href{http://bdtc2017.bigdataforum.org.cn/m/zone/bdtc2017/guest_detail?mid=1547&id=5932}{Deeplearning.scala - \footnotesize{Thoughts and practices on OSS AI framework}}}{DBTC}{}
	\twentyitem{2017}{\href{https://thestrangeloop.com/2017/monadic-deep-learning.html}{Monadic Deep Learning}}{Strange Loop}{}
	\twentyitem{2017}{\href{http://myslide.cn/slides/6644}{Neural Networks \& Functional Programming}}{ArchData Summit · Beijing}{}
	\twentyitem{2016}{\href{http://www.infoq.com/cn/presentations/more-than-async}{More than Async}}{QCon · Beijing}{}
	\twentyitem{2015}{\href{http://www.ecug.org/2015:home}{Specific-domain extension in an universal language}}{ECUG Con}{}
\end{twenty}



\section{Education}

\begin{twenty}
	\twentyitem{2002-2006}{Southwest University of Political Science and Law}{Bachelor Of Laws}{}
\end{twenty}
